---
title: "Programming Assignment 4"
author: "Monica Impaglia"
date: '2022-04-18'
output: github_document
---

## My Hypothesis 1:  I will finish this before midnight Monday##  
##  I do not have a hypothesis as far as the relationship of the VOT, F1, F2.  I am more focused on learning how to use R better##
```{r}
library("ggplot2")  
library("readr")  
library("here")  
library("tidyverse") 
library("dplyr")
library("purrr")  
```
```{r}
args(read.csv)  
read.csv(file = "C:\\Users\\Home\\OneDrive\\Desktop\\pa_4\\data\\bi01.csv") 
bi01 <- read.csv("C:\\Users\\Home\\OneDrive\\Desktop\\pa_4\\data\\bi01.csv")  
read.csv(file = "C:\\Users\\Home\\OneDrive\\Desktop\\pa_4\\data\\bi02.csv") 
bi02 <- read.csv("C:\\Users\\Home\\OneDrive\\Desktop\\pa_4\\data\\bi02.csv")
read.csv(file = "C:\\Users\\Home\\OneDrive\\Desktop\\pa_4\\data\\bi03.csv") 
bi03 <- read.csv("C:\\Users\\Home\\OneDrive\\Desktop\\pa_4\\data\\bi03.csv")
read.csv(file = "C:\\Users\\Home\\OneDrive\\Desktop\\pa_4\\data\\ne01.csv") 
ne01 <- read.csv("C:\\Users\\Home\\OneDrive\\Desktop\\pa_4\\data\\ne01.csv")
read.csv(file = "C:\\Users\\Home\\OneDrive\\Desktop\\pa_4\\data\\ne02.csv") 
ne02 <- read.csv("C:\\Users\\Home\\OneDrive\\Desktop\\pa_4\\data\\ne02.csv")
read.csv(file = "C:\\Users\\Home\\OneDrive\\Desktop\\pa_4\\data\\ne03.csv") 
ne03 <- read.csv("C:\\Users\\Home\\OneDrive\\Desktop\\pa_4\\data\\ne03.csv")

```

```{r} 
mean(bi01[1:3, "f1"])
```

```{r} 
mean(bi01[16:18, "f1"])
```

```{r}
mean(bi01[31:33, "f1"])
```
```{r}
bi01af1 <- c(691.47, 612.97, 553.42)  
mean(bi01af1)  
bi01_af1mean <- 619.2867
```
```{r}
mean(bi01[4:6, "f1"])
```
```{r}
mean(bi01[19:21, "f1"])
```

```{r}
mean(bi01[34:36, "f1"])
```
```{r}
bi01ef1 <- c(655.8533, 535.2233, 567.49)
mean(bi01ef1)
```
```{r}
bi01_ef1mean <- 586.1889
```

```{r}
mean(bi01[7:9, "f1"])
```
```{r}
mean(bi01[22:24, "f1"])
```

```{r}
mean(bi01[37:39, "f1"])
```
```{r}
bi01if1 <- c(555.2367, 369.14, 406.06) 
mean(bi01if1)  

```
```{r}
bi01_if1mean <- 443.4789
```
```{r}
mean(bi01[10:12, "f1"])
```
```{r}
mean(bi01[25:27, "f1"])
```

```{r}
mean(bi01[40:42, "f1"])
```
```{r}
bi01of1 <- c(537.1933, 460.66, 545.4533)  
mean(bi01of1)

```
```{r}
bi01_of1mean <- 514.4355  
```

```{r}
mean(bi01[13:15, "f1"])
```
```{r}
mean(bi01[28:30, "f1"])
```

```{r}
mean(bi01[43:45, "f1"])
```
```{r}  
bi01uf1 <- c(403.08, 433.5567, 479.96)
mean(bi01uf1)
bi01_uf1mean <- mean(bi01uf1)

```

```{r} 
mean(bi02[1:3, "f1"])
```

```{r} 
mean(bi02[16:18, "f1"])
```

```{r}
mean(bi02[31:33, "f1"])
```
```{r}
bi02af1 <- c(683.7833, 739.06,  696.9533)  
mean(bi02af1)  
bi02_af1mean <- 706.5989
```
```{r}
mean(bi02[4:6, "f1"])
```
```{r}
mean(bi02[19:21, "f1"])
```

```{r}
mean(bi02[34:36, "f1"])
```
```{r}
bi02ef1 <- c(485.8433, 483.2167, 461.56)
mean(bi01ef1)
```
```{r}
bi02_ef1mean <- 476.8733
```

```{r}
mean(bi02[7:9, "f1"])
```
```{r}
mean(bi02[22:24, "f1"])
```

```{r}
mean(bi02[37:39, "f1"])
```
```{r}
bi02if1 <- c(340.7233, 407.27, 501.7267) 
mean(bi02if1)  

```
```{r}
bi02_if1mean <- 416.5733
```
```{r}
mean(bi02[10:12, "f1"])
```
```{r}
mean(bi02[25:27, "f1"])
```

```{r}
mean(bi02[40:42, "f1"])
```
```{r}
bi02of1 <- c(560.7667, 576.15, 546.91)  
mean(bi02of1)

```
```{r}
bi02_of1mean <- 561.2756  
```

```{r}
mean(bi02[13:15, "f1"])
```
```{r}
mean(bi02[28:30, "f1"])
```

```{r}
mean(bi02[43:45, "f1"])
```
```{r}  
bi02uf1 <- c(411.26, 472.2267, 486.0433)
mean(bi02uf1)
bi02_uf1mean <- mean(bi01uf1)

```
```{r}
mean(bi03[1:3, "f1"])
mean(bi03[16:18, "f1"])
mean(bi03[31:33, "f1"])
bi03af1 <- c(mean(bi03[1:3, "f1"]), mean(bi03[16:18, "f1"]), mean(bi03[31:33, "f1"]))
bi03_af1mean <- mean(bi03af1)

```
```{r}
mean(bi03[4:6, "f1"])
mean(bi03[19:21, "f1"])
mean(bi03[34-36, "f1"])
bi03ef1 <- c(mean(bi03[4:6, "f1"]), mean(bi03[19:21, "f1"]), mean(bi03[34:36, "f1"]))
bi03_ef1mean <- mean(bi03ef1)

```
```{r}
mean(bi03[7:9, "f1"])
mean(bi03[22:24, "f1"])
mean(bi03[37:39, "f1"])
bi03if1 <- c(mean(bi03[7:9, "f1"]), mean(bi03[22:24, "f1"]), mean(bi03[37:39, "f1"]))
bi03_if1mean <- mean(bi03if1)

```

```{r}
mean(bi03[10:12, "f1"])
mean(bi03[25:27, "f1"])
mean(bi03[40:42, "f1"])
bi03of1 <- c(mean(bi03[10:12, "f1"]), mean(bi03[25:27, "f1"]), mean(bi03[40:42, "f1"]))
bi03_of1mean <- mean(bi03of1)

```
```{r}
mean(bi03[13:15, "f1"])
mean(bi03[28:30, "f1"])
mean(bi03[43:45, "f1"])
bi03uf1 <- c(mean(bi03[13:15, "f1"]), mean(bi03[28:30, "f1"]), mean(bi03[43:45, "f1"]))
bi03_uf1mean <- mean(bi03uf1)

```


```{r}
mean(ne01[1:3, "f1"])
mean(ne01[16:18, "f1"])
mean(ne01[31:33, "f1"])
ne01af1 <- c(mean(ne01[1:3, "f1"]), mean(ne01[16:18, "f1"]), mean(ne01[31:33, "f1"]))
ne01_af1mean <- mean(ne01af1)

```
```{r}
mean(ne01[4:6, "f1"])
mean(ne01[19:21, "f1"])
mean(ne01[34:36, "f1"])
ne01ef1 <- c(mean(ne01[4:6, "f1"]), mean(ne01[19:21, "f1"]), mean(ne01[34:36, "f1"]))
ne01_ef1mean <- mean(ne01ef1)

```
```{r}
mean(ne01[7:9, "f1"])
mean(ne01[22:24, "f1"])
mean(ne01[37:39, "f1"])
ne01if1 <- c(mean(ne01[7:9, "f1"]), mean(ne01[22:24, "f1"]), mean(ne01[37:39, "f1"]))
ne01_if1mean <- mean(ne01if1)

```

```{r}
mean(ne01[10:12, "f1"])
mean(ne01[25:27, "f1"])
mean(ne01[40:42, "f1"])
ne01of1 <- c(mean(ne01[10:12, "f1"]), mean(ne01[25:27, "f1"]), mean(ne01[40:42, "f1"]))
ne01_of1mean <- mean(ne01of1)

```
```{r}
mean(ne01[13:15, "f1"])
mean(ne01[28:30, "f1"])
mean(ne01[43:45, "f1"])
ne01uf1 <- c(mean(ne01[13:15, "f1"]), mean(ne01[28:30, "f1"]), mean(ne01[43:45, "f1"]))
ne01_uf1mean <- mean(ne01uf1)

```

```{r}
mean(ne02[1:3, "f1"])
mean(ne02[16:18, "f1"])
mean(ne02[31:33, "f1"])
ne02af1 <- c(mean(ne02[1:3, "f1"]), mean(ne02[16:18, "f1"]), mean(ne02[31:33, "f1"]))
ne02_af1mean <- mean(ne02af1)

```
```{r}
mean(ne02[4:6, "f1"])
mean(ne02[19:21, "f1"])
mean(ne02[34:36, "f1"])
ne02ef1 <- c(mean(ne02[4:6, "f1"]), mean(ne02[19:21, "f1"]), mean(ne02[34:36, "f1"]))
ne02_ef1mean <- mean(ne02ef1)

```
```{r}
mean(ne02[7:9, "f1"])
mean(ne02[22:24, "f1"])
mean(ne02[37:39, "f1"])
ne02if1 <- c(mean(ne02[7:9, "f1"]), mean(ne02[22:24, "f1"]), mean(ne02[37:39, "f1"]))
ne02_if1mean <- mean(ne02if1)

```

```{r}
mean(ne02[10:12, "f1"])
mean(ne02[25:27, "f1"])
mean(ne02[40:42, "f1"])
ne02of1 <- c(mean(ne02[10:12, "f1"]), mean(ne02[25:27, "f1"]), mean(ne02[40:42, "f1"]))
ne02_of1mean <- mean(ne02of1)

```
```{r}
mean(ne02[13:15, "f1"])
mean(ne02[28:30, "f1"])
mean(ne02[43:45, "f1"])
ne02uf1 <- c(mean(ne02[13:15, "f1"]), mean(ne02[28:30, "f1"]), mean(ne02[43:45, "f1"]))
ne02_uf1mean <- mean(ne02uf1)

```


```{r}
mean(ne03[1:3, "f1"])
mean(ne03[16:18, "f1"])
mean(ne03[31:33, "f1"])
ne03af1 <- c(mean(ne03[1:3, "f1"]), mean(ne03[16:18, "f1"]), mean(ne03[31:33, "f1"]))
ne03_af1mean <- mean(ne03af1)

```
```{r}
mean(ne03[4:6, "f1"])
mean(ne03[19:21, "f1"])
mean(ne02[34:36, "f1"])
ne03ef1 <- c(mean(ne03[4:6, "f1"]), mean(ne03[19:21, "f1"]), mean(ne03[34:36, "f1"]))
ne03_ef1mean <- mean(ne03ef1)

```
```{r}
mean(ne03[7:9, "f1"])
mean(ne03[22:24, "f1"])
mean(ne03[37:39, "f1"])
ne03if1 <- c(mean(ne03[7:9, "f1"]), mean(ne03[22:24, "f1"]), mean(ne03[37:39, "f1"]))
ne03_if1mean <- mean(ne03if1)

```

```{r}
mean(ne03[10:12, "f1"])
mean(ne03[25:27, "f1"])
mean(ne03[40:42, "f1"])
ne03of1 <- c(mean(ne03[10:12, "f1"]), mean(ne03[25:27, "f1"]), mean(ne03[40:42, "f1"]))
ne03_of1mean <- mean(ne03of1)

```
```{r}
mean(ne03[13:15, "f1"])
mean(ne03[28:30, "f1"])
mean(ne03[43:45, "f1"])
ne03uf1 <- c(mean(ne03[13:15, "f1"]), mean(ne03[28:30, "f1"]), mean(ne03[43:45, "f1"]))
ne03_uf1mean <- mean(ne03uf1)

```
```{r}
mean(bi01[1:15, "vot"])
bi01_meanvotK <- mean(bi01[1:15, "vot"])
mean(bi01[16:30, "vot"])  
bi01_meantvotP <- mean(bi01[16:30, "vot"]) 
mean(bi01[31:45, "vot"])
bi01_meanvotT <-  mean(bi01[31:45, "vot"])
```

```{r}
mean(bi02[1:15, "vot"])
bi02_meanvotK <- mean(bi02[1:15, "vot"])
mean(bi02[16:30, "vot"])  
bi02_meantvotP <- mean(bi02[16:30, "vot"]) 
mean(bi02[31:45, "vot"])
bi02_meanvotT <-  mean(bi02[31:45, "vot"])
```
```{r}
mean(bi03[1:15, "vot"])
bi03_meanvotK <- mean(bi03[1:15, "vot"])
mean(bi03[16:30, "vot"])  
bi03_meantvotP <- mean(bi03[16:30, "vot"]) 
mean(bi03[31:45, "vot"])
bi03_meanvotT <-  mean(bi03[31:45, "vot"])
```


```{r}
mean(ne01[1:15, "vot"])
ne01_meanvotK <- mean(ne01[1:15, "vot"])
mean(ne01[16:30, "vot"])  
ne01_meantvotP <- mean(ne01[16:30, "vot"]) 
mean(ne01[31:45, "vot"])
ne01_meanvotT <-  mean(ne01[31:45, "vot"])
```


```{r}
mean(ne02[1:15, "vot"])
ne02_meanvotK <- mean(ne01[1:15, "vot"])
mean(ne02[16:30, "vot"])  
ne02_meantvotP <- mean(ne02[16:30, "vot"]) 
mean(ne02[31:45, "vot"])
ne02_meanvotT <-  mean(ne02[31:45, "vot"])
```


```{r}
mean(ne03[1:15, "vot"])
ne03_meanvotK <- mean(ne03[1:15, "vot"])
mean(ne03[16:30, "vot"])  
ne03_meantvotP <- mean(ne03[16:30, "vot"]) 
mean(ne03[31:45, "vot"])
ne03_meanvotT <-  mean(ne03[31:45, "vot"])
```



```{r}
participant <- c("b1", "b2", "b3", "n1", "n2", "n3")
f1a <- c(bi01_af1mean, bi02_af1mean, bi03_af1mean, ne01_af1mean, ne02_af1mean, ne03_af1mean)
f1e <- c(bi01_ef1mean, bi02_ef1mean, bi03_ef1mean, ne01_ef1mean, ne02_ef1mean, ne03_ef1mean)
f1i <- c(bi01_if1mean, bi02_if1mean, bi03_if1mean, ne01_if1mean, ne02_if1mean, ne03_if1mean)
f1o <- c(bi01_of1mean, bi02_of1mean, bi03_of1mean, ne01_of1mean, ne02_of1mean, ne03_of1mean)
f1u <- c(bi01_uf1mean, bi02_uf1mean, bi03_uf1mean, ne01_uf1mean, ne02_uf1mean, ne03_uf1mean)
votK <- c(bi01_meanvotK, bi02_meanvotK, bi03_meanvotK, ne01_meanvotK, ne02_meanvotK, ne03_meanvotK)
votP <- c(bi01_meantvotP, bi02_meantvotP, bi03_meantvotP, ne01_meantvotP, ne02_meantvotP, ne03_meantvotP)
votT <- c(bi01_meanvotT, bi02_meanvotT, bi03_meanvotT, ne01_meanvotT, ne02_meanvotT, ne03_meanvotT)  
all_participants <- data.frame(participant, f1a, f1e, f1i, f1o, f1u, votK, votP, votT)



```
```{r}
ggplot(data = all_participants, aes(x = votK, y = f1a, color = participant)) +  
  geom_point()  
```
```{r}
ggplot(data = all_participants, aes(x = votK, y = f1e, color = participant)) +  
  geom_point()  
```

```{r}
ggplot(data = all_participants, aes(x = votK, y = f1i, color = participant)) +  
  geom_point()  
```

```{r}
ggplot(data = all_participants, aes(x = votK, y = f1o, color = participant)) +  
  geom_point()  
```
```{r}
ggplot(data = all_participants, aes(x = votK, y = f1u, color = participant)) +  
  geom_point()  
```

```{r}
ggplot(data = all_participants, aes(x = votP, y = f1a, color = participant)) +  
  geom_point()  
```
```{r}
ggplot(data = all_participants, aes(x = votP, y = f1e, color = participant)) +  
  geom_point()  
```

```{r}
ggplot(data = all_participants, aes(x = votP, y = f1i, color = participant)) +  
  geom_point()  
```

```{r}
ggplot(data = all_participants, aes(x = votP, y = f1o, color = participant)) +  
  geom_point()  
```
```{r}
ggplot(data = all_participants, aes(x = votP, y = f1u, color = participant)) +  
  geom_point()  
```

```{r}
ggplot(data = all_participants, aes(x = votT, y = f1a, color = participant)) +  
  geom_point()  
```
```{r}
ggplot(data = all_participants, aes(x = votT, y = f1e, color = participant)) +  
  geom_point()  
```

```{r}
ggplot(data = all_participants, aes(x = votT, y = f1i, color = participant)) +  
  geom_point()  
```

```{r}
ggplot(data = all_participants, aes(x = votT, y = f1o, color = participant)) +  
  geom_point()  
```
```{r}
ggplot(data = all_participants, aes(x = votT, y = f1u, color = participant)) +  
  geom_point()  
```


## My original hypothesis of finishing pa_4 before midnight on Monday was incorrect.  On the other hand, I am very happy and proud of my progress in using R.  I was able to manipulate the data in my .csv files to find means of specific sections, then create a new data frame from those means and plot the resulting data.##























